\section{Self - Summary}

\subsection{What I learned}
\begin{itemize}
	\item \textbf{Data Structures and Algorithms:} I have learned about the basic data structures and algorithms, such as arrays, linked lists, stacks, queues, trees, graphs, searching, and sorting algorithms. I have also learned about the time complexity and space complexity of these algorithms.
	\item \textbf{Problem-solving skills:} I have learned how to solve problems using data structures and algorithms. I have also learned how to analyze the time complexity and space complexity of algorithms.
	\item \textbf{Programming skills:} I have improved my programming skills by implementing various data structures and algorithms in C++ and Python.
	\item \textbf{Front-end development:} I have learned how to create a simple web application using HTML, CSS, and JavaScript.
	\item \textbf{Version control:} I have learned how to use Git and GitHub for version control. And I stored my code in my personal repository.
\end{itemize}

\subsection{What was my difficult}
\begin{itemize}
	\item \textbf{Time management:} I found it challenging to manage my time effectively to complete the assignments and projects on time.
	\item \textbf{Understanding complex algorithms:} I found it challenging to understand some complex algorithms, such as dynamic programming and graph algorithms.
	\item \textbf{Debugging:} I found it challenging to debug my code when it did not work as expected.
	\item \textbf{Language barrier:} I found it challenging to understand some of the lectures and materials due to the language barrier.
	\item \textbf{Lack of practice:} I found it challenging to practice regularly to improve my problem-solving and programming skills.
\end{itemize}